A finite-state morphological transducer for Kyrgyz

### 2012-03-13 paper/paper.tex
updates

\section{Description}
%FIXME: \ldots{} section
The tagset consists of 119 separate tags, 17 covering the main parts of speech (noun, verb, adjective, adverb, postposition, \ldots{}) and 102 covering morphological subcategorisation for e.g. case, number, person, possession, transitivity, tense-aspect-mood, etc.

The tags are represented as multicharacter symbols, between `<' and `>' punctuation.

@@

\subsection{Coverage}

%FIXME: is this about right?  and I mean all aspects of the paragraph
%FIXME: ZZ needs to be replaced with .. ?
To calculate the naïve coverage\footnote{FIXME} of the analyser, two corpora were used, the first was a database dump of the Kyrgyz Wikipedia, dated 2011-09-23,\footnote{The exact name of the dump was \texttt{kywiki-20110923-pages-articles.xml}.} which was processed with the programs \texttt{aq-wikicrp} and ZZ to extract sentences. The second was a corpus generated from the archives of Radio Free Europe / Radio Liberty's Kyrgyz service, \href{http://www.azattyk.org}{azattyk.org}.  The RFERL corpus was built using a script that scraped the archives for all articles from 2010, which include articles on a wide variety of topics, from sports to politics and from culture to current events.

@@

>>>>

\section{Description}
%FIXME: \ldots{} section
The tagset consists of 127 separate tags, 19 covering the main parts of speech (noun, verb, adjective, adverb, postposition, etc.) and 108 covering morphological subcategorisation for e.g. case, number, person, possession, transitivity, tense-aspect-mood, etc. The tags are represented as multicharacter symbols, between less than `<' and greater than `>' symbols. The tagset is quite extensive and still not entirely stabilised, as such a full listing is not included here. However, the tags are listed in the source code of the transducer, along with comments describing their usage.

@@

\section{Evaluation}

We have evaluated the analyser in two ways. The first is by calculating the naïve coverage and mean ambiguity 
on two large freely available corpora of Kyrgyz. The second is by performing an evaluation of precision and recall on a smaller, hand-validated test set.

\subsection{Coverage and mean ambiguity}

%FIXME: is this about right?  and I mean all aspects of the paragraph
%FIXME: ZZ needs to be replaced with .. ?
To calculate the naïve coverage\footnote{The naïve coverage is the percentage of surface forms that receive at least one analysis. This may not be complete.} of the analyser, two corpora were used, the first was a database dump of the Kyrgyz Wikipedia, dated 2011-09-23,\footnote{The exact name of the dump was \texttt{kywiki-20110923-pages-articles.xml}.} which was processed with the programs \texttt{aq-wikicrp} and ZZ to extract sentences. The second was a corpus generated from the archives of Radio Free Europe / Radio Liberty's Kyrgyz service, \href{http://www.azattyk.org}{azattyk.org}.  The RFERL corpus was built using a script that scraped the archives for all articles from 2010, which include articles on a wide variety of topics, from sports to politics and from culture to current events.

@@

\subsection{Precision and recall}

To calculate precision and recall, it was necessary to create a hand-verified list of surface forms and their analyses.
